Structuring College Access

### 2025-02-18 index.qmd
tweakin

::: {.column width="50%"}
**[University of Chicago admissions counselors, Chicago-land](https://collegeadmissions.uchicago.edu/contact)**
![](./assets/images/chicagoland_territories_u_chicago_redacted.png)
:::
:::

>>>>

::: {.column width="50%"}
**[University of Chicago admissions counselors, IL territories](https://collegeadmissions.uchicago.edu/contact)**
![](./assets/images/chicagoland_territories_u_chicago_redacted.png)
:::
:::
